---
title: "Explore modeling possibilities for the modeling paper"
output: rmarkdown::pdf_document

---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.height = 7,
  fig.width = 8,
  echo = FALSE
)
```

```{r setup}



library(data.intercrop)
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
library(stringr)
library(kclique)
# devtools::install_github("RemiMahmoud/functions.helper")
library(functions.helper)
library(Bolstad)


theme_set(theme_bw() + theme(legend.position = "bottom", legend.title = element_blank()))

# Set wd to project source
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```


```{r useful functions}


collapse_unique <- function (x, collapse_character = "_") 
{
    ifelse(is.numeric(x), sum(unique(x)), paste(unique(x), collapse = collapse_character))
}
```

```{r}
function_all_steps_kclique <- function(dat, format_kclique = "wide"){
  
  G <- get_graph_from_dat(dat)
  kcliques <- maximal_kclique_enumeration(G, dat)
  tibble_kclique <- function_list_kcliques_to_tibble(kcliques, dat, format = format_kclique)
  
  return(list(tibble_kclique = tibble_kclique, G = G))


}



```




# Set data of all experiments

```{r}

traits <- data.intercrop::traits$plot

traits_crop <- data.intercrop::traits$crop




experiments_paper <- data.intercrop::index %>% filter(species_mix %in% c("wheat_turgidum_pea", "wheat_turgidum_fababean") ) %>% distinct(experiment_id, species_mix)

index_paper <- data.intercrop::index %>% inner_join(experiments_paper)


data_flowering <- traits_crop %>% filter(str_detect(variable, "BBCH_6.*")) %>% inner_join(experiments_paper) %>% distinct(experiment_id, variable,  time_flowering = time_sowing, date_flowering = date, time_thermal_flowering = time_thermal, species, species_mix ,crop_id) %>% rename("pheno_stage" = variable)


```


# Explore combinations of experiments and plant variables


<!-- ## Practices -->


```{r, eval = FALSE}


cultivar_paper <- index_paper %>% distinct(cultivar_mix, species_mix, experiment_id) %>% separate(cultivar_mix, into = c("cult_cereal", "cult_legume"))
cultivar_wt_pea <- cultivar_paper %>% filter(species_mix == "wheat_turgidum_pea") %>% select(-species_mix)
cultivar_wt_fababean <- cultivar_paper %>% filter(species_mix == "wheat_turgidum_fababean") %>% select(-species_mix)



graph_cultivars_wt_pea <- function_all_steps_kclique(cultivar_wt_pea)

plot_graph(graph_cultivars_wt_pea$G,cultivar_wt_pea)

graph_cultivars_wt_fababean <- function_all_steps_kclique(cultivar_wt_fababean)

plot_graph(graph_cultivars_wt_fababean$G,cultivar_wt_fababean)

plot_kclique(graph_cultivars_wt_fababean$G, graph_cultivars_wt_fababean$tibble_kclique, cultivar_wt_fababean, 3) +  theme(legend.title = element_blank())
plot_kclique(graph_cultivars_wt_pea$G, graph_cultivars_wt_pea$tibble_kclique, cultivar_wt_pea, 5)+  theme(legend.title = element_blank())


index_paper %>% filter(cultivar_mix == "nefer_lucy") %>% distinct(experiment_id, management, N_amount)
```






```{r, eval = FALSE}

# 
# G <- kclique::get_graph_from_dat(experiments_paper)
# kclique_experiments <- kclique::maximal_kclique_enumeration(G, experiments_paper)
# tibble_kclique <- kclique::function_list_kcliques_to_tibble(kclique_experiments, dat = experiments_paper)
# 
# plot_kclique(G, tibble_kclique, experiments_paper, vector_kcliques = 1)
# plot_kclique(G, kclique_experiments, dataset = experiments_paper, vector_kcliques = 1)
# 
# plot_kclique(G, kclique_experiments, dataset = experiments_paper, vector_kcliques = 3)
# 

```



```{r}


data_variables_experiment_paper <- data.intercrop::traits_mean %>% inner_join(experiments_paper) %>% filter(crop_type == "IC") %>% distinct(experiment_id,  species_mix, variable) %>% filter(!str_detect(variable, "BBCH|density|aphids|nitrogen|phosphorus.*_seed|senesc|ndfa|biomass_seed|biomass_leaf.*|tkw|stem|phosphorus_abs|biomass_greenleaf|greenleaf_number|leaf_layer|fruit_layer|flower_layer|reproductive_organ_number|carbon_abs_shoot|carbon_seed|carbon_veg|sla_greenleaf$")) %>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C")))

```


### Durum wheat / fababean

Here is the graph connecting the experimental units and the measured variables in experiments including durum wheat / fababean mixtures. Some variables are only measured once (leaf_number, P in shoot parts etc.).


```{r}
data_variables_fababean <- data_variables_experiment_paper %>% filter(species_mix == "wheat_turgidum_fababean")

result_fababean <- function_all_steps_kclique(data_variables_fababean %>% select(-species_mix))
plot_graph(result_fababean$G, data_variables_fababean)

```


If we compute all the kcliques within this graph, we get 3 kcliques with 4 experiments or more. We select the kclique with id 3 which contains 54 observations and 6 variables, and 4 out of 5 expeirments including durum wheat and fababean:

* Shoot's biomass
* Branching
* Cover
* LAI
* Height
* Specific leaf area (green leaves)

```{r}
# result_fababean$tibble_kclique


tibble_kclique_long_wt_fababean <- function_all_steps_kclique(data_variables_fababean, format_kclique = "long")$tibble_kclique %>% group_by(kclique_id) %>% mutate(n_experiments = length(unique(experiment_id))) %>% ungroup %>% filter(n_experiments >= 4)


n_ue_by_experiment_wt_fababean <- traits_mean %>% filter(crop_type  == 'IC', species_mix == "wheat_turgidum_fababean") %>% distinct(experiment_id, management, variable)%>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  inner_join(tibble_kclique_long_wt_fababean %>% distinct(experiment_id)) %>% 
  distinct(experiment_id, management) %>% 
  count(experiment_id, name = "n_ue")

summary_by_kclique_wt_fababean <- traits_mean %>% filter(crop_type  == 'IC', species_mix == "wheat_turgidum_fababean") %>% distinct(experiment_id, management, variable)%>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  inner_join(tibble_kclique_long_wt_fababean %>% distinct(experiment_id, variable, kclique_id)) %>% 
  count(experiment_id, variable, kclique_id) %>% left_join(n_ue_by_experiment_wt_fababean) %>% mutate(perc_measure_variable  = n/n_ue)

summary_by_kclique_wt_fababean %>% 
  group_by(kclique_id) %>% 
  summarise(n_experiments = length(unique(experiment_id)),n_variables = length(unique(variable)), n_obs = sum(unique(n_ue)), variables = collapse_unique(variable)) %>% kable


plot_kclique_fababean <- plot_kclique(result_fababean$G, tibble_kcliques = result_fababean$tibble_kclique, dataset = data_variables_fababean, vector_kcliques = 3, size_text = 3)+ ggthemes::theme_solarized() + theme(legend.position = "none", axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank())

ggsave("figures/plot_kclique_wt_fababean.png", plot = plot_kclique_fababean, height = 18,width =14.5, unit = "cm", dpi = 350)



# data_variable_wt_fababean <- summary_by_kclique_wt_fababean %>%
#   filter(kclique_id == "3") %>%
#   distinct(variable, experiment_id)


data_variable_wt_fababean <- summary_by_kclique_wt_fababean %>% 
  filter(kclique_id == "3") %>% 
  distinct(variable, experiment_id)

```


### Explore data durum wheat / fababean



Here are the evolutions of each selected variables (except height and biomass, treated in other documents). Dashed lines are the flowering times. 

```{r}


data_explore_wt_fababean <- traits_mean %>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  filter(crop_type  == 'IC', species_mix == "wheat_turgidum_fababean") %>% 
  distinct(experiment_id, management,crop_id, species, variable, value, time_thermal, time_sowing, N_amount) %>%
  inner_join(data_variable_wt_fababean) %>% 
  filter(!(variable %in% c("height", "biomass_shoot"))) 

data_explore_wt_fababean %>% 
  left_join(data_flowering) %>% 
  # filter(variable == "lai" | variable == "cover") %>% 
  ggplot(aes(x = time_sowing, y = value, color = species)) +
  geom_point(alpha = .4) + 
  geom_line(alpha=  .4, aes(group = crop_id ))+
  geom_vline(aes(xintercept = time_flowering, color = species), alpha = .5 , linetype = "dashed") + 
  facet_grid(variable ~experiment_id, scales = "free") 
  # facet_wrap(variable~. , scales = "free")
```






## Durum wheat / pea


Here is the graph connecting the experimental units and the measured variables in experiments including durum wheat / pea mixtures. Variables are mostly measured in 3 or 4 experiments.


```{r}
data_variables_pea <- data_variables_experiment_paper %>% filter(species_mix == "wheat_turgidum_pea")

result_pea <- function_all_steps_kclique(data_variables_pea %>% select(-species_mix))
plot_graph(result_pea$G, data_variables_pea)
# result_pea$tibble_kclique


```

We select the kclique with id 8 as it contains 6 variables and 47 observations, especially LAI.

```{r}


tibble_kclique_long_wt_pea <- function_all_steps_kclique(data_variables_pea, format_kclique = "long")$tibble_kclique %>% group_by(kclique_id) %>% mutate(n_experiments = length(unique(experiment_id))) %>% ungroup %>% filter(n_experiments >= 4)


n_ue_by_experiment_wt_pea <- traits_mean %>% filter(crop_type  == 'IC', species_mix == "wheat_turgidum_pea") %>% distinct(experiment_id, management, variable)%>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  inner_join(tibble_kclique_long_wt_pea %>% distinct(experiment_id)) %>% 
  distinct(experiment_id, management) %>% 
  count(experiment_id, name = "n_ue")

summary_by_kclique_wt_pea <- traits_mean %>% filter(crop_type  == 'IC', species_mix == "wheat_turgidum_pea") %>% distinct(experiment_id, management, variable)%>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  inner_join(tibble_kclique_long_wt_pea %>% distinct(experiment_id, variable, kclique_id)) %>% 
  count(experiment_id, variable, kclique_id) %>% left_join(n_ue_by_experiment_wt_pea) %>% mutate(perc_measure_variable  = n/n_ue)

# summary_by_kclique_wt_pea %>% 
#   group_by(kclique_id) %>% 
#   summarise(n_experiments = length(unique(experiment_id)),n_variables = length(unique(variable)), n_obs = sum(unique(n_ue))) %>% 
#   kable


summary_by_kclique_wt_pea %>% 
  group_by(kclique_id) %>% 
  summarise(n_experiments = length(unique(experiment_id)),n_variables = length(unique(variable)), n_obs = sum(unique(n_ue)), variables = collapse_unique(variable)) %>% kable


# plot_kclique_pea <- plot_kclique(result_pea$G, tibble_kcliques = result_pea$tibble_kclique, dataset = data_variables_pea, vector_kcliques = 8, size_text = 3) + ggthemes::theme_solarized() + theme(legend.position = "none", axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank())
# #
# ggsave("figures/plot_kclique_wt_pea.png", plot = plot_kclique_pea, height = 18,width =14.5, unit = "cm", dpi = 350)




data_variable_wt_pea <- summary_by_kclique_wt_pea %>% 
  filter(kclique_id == "8") %>% 
  distinct(variable, experiment_id)
```

### Explore data durum wheat / pea

Here are the evolutions of each selected variables (except height and biomass, treated in other documents). Dashed lines are the flowering times.  

variable | meaning
------------- | -------------
sla_GLT | specific leaf area (with tendrils or pods)
lai  | leaf area index 


```{r}


data_explore_wt_pea <- traits_mean %>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  filter(crop_type  == 'IC', species_mix == "wheat_turgidum_pea") %>%
  distinct(experiment_id, management,crop_id, species,  variable, value, time_thermal, time_sowing, N_amount) %>%
  inner_join(data_variable_wt_pea) %>% 
  filter(!(variable %in% c("height", "biomass_shoot", "C_shoot"))) 

data_explore_wt_pea %>%
  left_join(data_flowering) %>% 
  filter(variable != "C_shoot") %>%
  ggplot(aes(x = time_sowing, y = value)) +
  geom_point(alpha = .4) + 
  geom_line(alpha=  .4, aes(group = crop_id , color = species))+
  geom_vline(aes(xintercept = time_flowering, color = species), alpha = .5 , linetype = "dashed") + 
  facet_grid(variable ~experiment_id, scales = "free") 
  # facet_wrap(variable~. , scales = "free")


# data_explore_wt_pea %>% 
#   filter(variable == "cover") %>%
#   ggplot(aes(x = time_sowing, y = value)) +
#   geom_point(alpha = .4) + 
#   geom_line(alpha=  .4, aes(group = crop_id , color = management))+
#   facet_grid(variable ~experiment_id, scales = "free") 
  # facet_wrap(variable~. , scales = "free")

```


### Extract meaningful information from the data

Specific leaf area index will be summarised by taking the maximal value during the crop cycle. Differences between species and IC-SC will be computed.

In these experiments, flowering dates are available, which allows us to compute differences between LAI at flowering date of the legume and the cereal. 

Cover are measured frequently, we may take the integral during the crop cycle to correlate it with the yield and other performance measures (CE, SE, PLER).



## Bivariate relationships 



```{r, eval = TRUE}

trapeze_integration <- function(data, var_time = "time_sowing"){
  # if((dim(vec)[2] >1)){warning("multiple columns, taking the first colum as vector to integrate")
  #   vec = vec[,1]
  #   }
  
  vec_time = data[[var_time]]
  vec_values = data[[ "value"]]
  n <- length(vec_time)
  
  a = min(vec_time)
  b = max(vec_time)
  
  if(n == 1){ 
    warning("only one point, returning value as integral")
    return(data[["value"]])}
  
  if(n == 2){ 
    warning("only 2 points, returning mean as integral")
    return( 0.5*(b-a)*sum(vec_values))}
  
  n_pts <- 2*256 +1  
  ap <- approx(vec_time, vec_values, n = n_pts)
  # return( ((b-a)/n)*(0.5*(vec_values[1] + vec_values[n]) + sum(vec_values[2:(n-1)]))   )
  return(((b-a)/n_pts)* (0.5*ap$y[1] + ap$y[n_pts] + sum( ap$y[2:(n_pts -1 )])))
  
}


simpson_integration <- function(data, var_time = "time_sowing"){
  vec_time = data[[var_time]]
  vec_values = data[[ "value"]]
  n <- length(vec_time)
  
  a = min(vec_time)
  b = max(vec_time)
  
  if(n == 1){ 
    warning("only one point, returning value as integral")
    return(data[["value"]])}
  
  if(n == 2){ 
    warning("only 2 points, returning mean as integral")
    return( 0.5*(b-a)*sum(vec_values))}
  
  return( sintegral(vec_time, vec_values, n.pts = n)$value  )
}



```


### LAI

Max LAI seems to be a good predictor for yield. 

```{r}


data_explore <- bind_rows(data_explore_wt_fababean,data_explore_wt_pea)


traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "lai" | variable == "biomass_seed") %>%
  distinct(crop_id,experiment_id, variable, value, species,time_sowing, crop_type) %>% 
  group_by(experiment_id,crop_id, species, variable, crop_type) %>% 
  summarise(max = max(value), .groups = "drop") %>% 
  pivot_wider(names_from = variable, values_from = max) %>% 
  ggplot(aes(x = lai, y = biomass_seed)) +
  geom_point(alpha=  .4, aes( color = species)) + 
  labs(x = "max_LAI", y ="Yield") + 
  geom_line(aes(group = species, color = species), method = "lm", se = TRUE, alpha= .6, stat ="smooth") +
  geom_smooth (aes(group = species, color = species), alpha=0.2, size=0, method = "lm") + 
  # stat_smooth(geom = "smooth", method = "lm", alpha = .4, aes(group = species, color = species), ) + 
  facet_wrap(experiment_id~.)



```


### Integral cover

Relationships are weaker with cover integral


```{r, warning=FALSE}

data_integral_cover_nest <- traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species))  %>% 
  filter(variable == "cover") %>%
  select(experiment_id, crop_id, variable, value, time_sowing) %>% 
  filter(!is.na(value)) %>% 
  arrange(experiment_id, crop_id, time_sowing) %>%
  # select(-time_sowing) %>% 
  group_by(experiment_id, crop_id, variable) %>% 
  nest() %>% 
  ungroup %>%
  # mutate(data = purrr::map(data, unlist)) %>%
  mutate(integral_cover = purrr::map(data, trapeze_integration), integral_cover_simpson = purrr::map(data, simpson_integration), n_points = purrr::map(data, nrow))


data_integral_cover <- data_integral_cover_nest %>% unnest(c(integral_cover, integral_cover_simpson,n_points)) 


traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "biomass_seed") %>%
  distinct(crop_id,experiment_id, variable, value, species,time_sowing, crop_type) %>% 
  group_by(experiment_id,crop_id, species, variable, crop_type) %>% 
  summarise(max = max(value), .groups = "drop") %>% 
  pivot_wider(names_from = variable, values_from = max) %>% 
  left_join(data_integral_cover %>% distinct(crop_id, integral_cover)) %>% 
  ggplot(aes(x = integral_cover, y = biomass_seed)) +
  geom_point(alpha=  .4, aes( color = species)) + 
  labs(x = "Integral cover", y ="Yield") + 
  geom_line(aes(group = species, color = species), method = "lm", se = TRUE, alpha= .6, stat ="smooth") +
  geom_smooth (aes(group = species, color = species), alpha=0.2, size=0, method = "lm") + 
  # stat_smooth(geom = "smooth", method = "lm", alpha = .4, aes(group = species, color = species), ) + 
  facet_wrap(experiment_id~., scales = "free")
```


### Specific Leaf Area

No clear strong relationship between max SLA and yield.

```{r, warning=FALSE}




traits_mean %>%
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT"))) %>% 
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "sla_GLT" | variable == "biomass_seed") %>%
  distinct(crop_id,experiment_id, variable, value, species,time_sowing, crop_type) %>% 
  group_by(experiment_id,crop_id, species, variable, crop_type) %>% 
  summarise(max = max(value), .groups = "drop") %>% 
  pivot_wider(names_from = variable, values_from = max) %>% 
  ggplot(aes(x = sla_GLT, y = biomass_seed)) +
  geom_point(alpha=  .4, aes( color = species)) + 
  labs(x = "max_sla_GLT", y ="Yield") + 
  geom_line(aes(group = species, color = species), method = "lm", se = TRUE, alpha= .6, stat ="smooth") +
  geom_smooth (aes(group = species, color = species), alpha=0.2, size=0, method = "lm") + 
  # stat_smooth(geom = "smooth", method = "lm", alpha = .4, aes(group = species, color = species), ) + 
  facet_wrap(experiment_id~., scales ="free")



```



```{r pb C shoot, eval = FALSE}


traits_mean %>% 
  mutate(variable = str_replace_all(variable, c("greenleaftendril" = "GLT", "phosphorus" = "P", "carbon" = "C"))) %>% 
  filter(variable == "C_shoot") %>%
  distinct(experiment_id, management,crop_id, species,  variable, value, time_thermal, time_sowing, N_amount)  %>% 
  ggplot(aes(x = time_sowing, y = value)) +
  geom_point(alpha = .4) + 
  geom_line(alpha=  .4, aes(group = crop_id , color = species))+
  labs(y= "Carbon content in shoots") +
  facet_grid(species ~experiment_id, scales = "free") 
  facet_wrap(variable~. , scales = "free")


data_pb_C_shoot <- traits_mean %>% 
  filter(variable == "carbon_shoot", experiment_id == "Auzeville_SGs_2007") %>% 
  distinct(experiment_id, management, species,date, time_sowing,  value)

# readr::write_delim(data_pb_C_shoot, path = "../modeling_intercrop/data_pb_C_shoot.xlsx", delim = ";")
```



<!-- ## Integration LAI -->



```{r, eval = FALSE}

data_explore_wt_pea %>% 
  left_join(data_integral_lai) %>% 
  filter(variable == "lai") %>%
  ggplot(aes(x = time_sowing, y = value)) +
  geom_point(alpha = .4, aes(shape = species)) + 
  geom_line(alpha=  .4, aes(group = crop_id , color = integral_lai))+
  facet_grid(variable ~experiment_id, scales = "free") + 
  scale_color_continuous(low = "blue",  high= "red")
  # facet_wrap(variable~. , scales = "free")
```


```{r, eval= FALSE}



data_explore_wt_pea %>% 
  inner_join(data_flowering) %>% 
  # filter(variable == "lai") %>%
  filter(variable != "C_shoot") %>% 
  ggplot(aes(x = time_sowing, y = value)) +
  geom_point(alpha = .4, aes(color = species)) + 
  geom_line(alpha=  .4, aes(group = crop_id ))+
  geom_vline(aes(xintercept = time_flowering, color = species)) + 
  facet_grid(variable ~experiment_id, scales = "free") 


data_explore_wt_fababean %>% 
  inner_join(data_flowering) %>% 
  # filter(variable == "lai") %>%
  filter(variable != "C_shoot") %>% 
  ggplot(aes(x = time_sowing, y = value)) +
  geom_point(alpha = .4, aes(color = species)) + 
  geom_line(alpha=  .4, aes(group = crop_id ))+
  geom_vline(aes(xintercept = time_flowering, color = species)) + 
  facet_grid(variable ~experiment_id, scales = "free") 

data_explore_wt_fababean %>% 
  inner_join(data_flowering) %>% 
  filter(variable == "lai") %>%
  # filter(variable != "C_shoot") %>% 
  ggplot(aes(x = time_sowing, y = value)) +
  geom_point(alpha = .7, aes(color = species)) + 
  geom_line(alpha=  .4, aes(group = crop_id ))+
  geom_vline(aes(xintercept = time_flowering, color = species), alpha=  .6, linetype = "dashed") + 
  facet_grid(variable ~experiment_id, scales = "free") 




```


```{r lai SC vs lai IC, eval = FALSE}

data_explore <- bind_rows(data_explore_wt_fababean,data_explore_wt_pea)

traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "lai" | variable == "biomass_seed") %>% 
  ggplot(aes(x = species, y = value, fill = crop_type)) + 
  geom_boxplot(alpha = .3, outlier.size=  0) + 
  geom_point(position =  position_jitterdodge(jitter.width = 0.2), pch = 21) + 
  facet_wrap(experiment_id~., scales= "free")

traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "cover") %>% 
  ggplot(aes(x = species, y = value, fill = crop_type)) + 
  geom_boxplot(alpha = .3, outlier.size=  0) + 
  geom_point(position =  position_jitterdodge(jitter.width = 0.2), pch = 21) + 
  facet_wrap(experiment_id~., scales= "free")



traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "lai" | variable == "biomass_seed") %>%
  distinct(crop_id,experiment_id, variable, value, species,time_sowing, crop_type) %>% 
  group_by(experiment_id,crop_id, species, variable, crop_type) %>% 
  summarise(max = max(value), .groups = "drop") %>% 
  pivot_wider(names_from = variable, values_from = max) %>% 
  ggplot(aes(x = lai, y = biomass_seed)) +
  geom_point(alpha=  .4, aes( color = species)) + 
  geom_smooth(aes(group = species, color = species), method = "lm", se = FALSE, alpha= .3) + 
  facet_wrap(experiment_id~.)





data_integral_lai_nest <- traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species))  %>% 
  filter(variable == "lai") %>%
  select(experiment_id, crop_id, variable, value, time_sowing) %>% 
  filter(!is.na(value)) %>% 
  arrange(experiment_id, crop_id, time_sowing) %>%
  # select(-time_sowing) %>% 
  group_by(experiment_id, crop_id, variable) %>% 
  nest() %>% 
  ungroup %>%
  # mutate(data = purrr::map(data, unlist)) %>%
  mutate(integral_lai = purrr::map(data, trapeze_integration), integral_lai_simpson = purrr::map(data, simpson_integration), n_points = purrr::map(data, nrow))


data_integral_lai <- data_integral_lai_nest %>% unnest(c(integral_lai, integral_lai_simpson,n_points)) 


traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "lai" | variable == "biomass_seed") %>%
  distinct(crop_id,experiment_id, variable, value, species,time_sowing, crop_type) %>% 
  group_by(experiment_id,crop_id, species, variable, crop_type) %>% 
  summarise(max = max(value), .groups = "drop") %>% 
  pivot_wider(names_from = variable, values_from = max, names_prefix = "max_") %>% 
  left_join(data_integral_lai %>% distinct(crop_id, integral_lai)) %>% 
  pivot_longer(contains("lai"), values_to = "lai", names_to = "type") %>% 
  ggplot(aes(x = lai, y = max_biomass_seed)) +
  geom_point(alpha=  .4, aes( color = type)) + 
  # geom_smooth(aes(group = species, color = species), method = "lm", se = FALSE, alpha= .3) + 
  facet_grid(experiment_id~type, scales= "free")


data_cor <- traits_mean %>%
  inner_join(data_explore %>% distinct(experiment_id, species)) %>% 
  filter(variable == "lai" | variable == "biomass_seed") %>%
  distinct(crop_id,experiment_id, variable, value, species,time_sowing, crop_type) %>% 
  group_by(experiment_id,crop_id, species, variable, crop_type) %>% 
  summarise(max = max(value), .groups = "drop") %>% 
  pivot_wider(names_from = variable, values_from = max, names_prefix = "max_") %>% 
  left_join( data_integral_lai %>% distinct(crop_id, integral_lai)) %>% 
  select( contains("lai"), max_biomass_seed, species)


GGally::ggpairs(data_cor, aes(color = species))
```










