---
title: "Get control managements for each experimental unit of the dataset"
output: rmarkdown::pdf_document

---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r setup}



library(data.intercrop)
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)

# devtools::install_github("RemiMahmoud/functions.helper")
library(functions.helper)

theme_set(theme_bw())

# Set wd to project source
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```


```{r useful functions}


collapse_unique <- function (x, collapse_character = "_") 
{
    ifelse(is.numeric(x), sum(unique(x)), paste(unique(x), collapse = collapse_character))
}
```


In this file, we find the corresponding SC treatment for each IC treatment of the datasets



# Set data of all experiments

```{r}

traits <- data.intercrop::traits$plot

traits_crop <- data.intercrop::traits$crop


#Look at experiments for which there is more than 1 measure of biomass
# traits %>%
#   filter(variable == "biomass_seed") %>%
#   count(experiment_id, management, rep_number, species) %>%
#   filter(n > 1)



data_work_yield <- traits %>% 
  filter(variable == "biomass_seed") %>% 
  distinct(experiment_id, management, crop_type,plant_family, species, cultivar, density_factor, density_level, N_factor, N_amount, P_amount, interrow)

data_work_yield_crop <- traits_crop %>% 
  
  filter(variable == "biomass_seed") %>% 
  distinct(experiment_id, management, crop_type, plant_family, species, cultivar, density_factor, density_level, N_factor, N_amount, P_amount, interrow)


```



For each IC management, we look to have a "control" management in SC, that is a management in SC with the same:

* experiment_id
* cultivar
* N_factor
* N_amount
* P_amount (when provided)
* Interrow distance

We also look to have a control management in SC but with no N fertilisation (N0).
```{r set references SC plot}

data_work_control <- data_work_yield %>% 
  #GET MANAGEMENT CONTROL IN SC
  group_by(experiment_id,
           cultivar,
           N_factor,
           N_amount,
           interrow,
           P_amount) %>% 
  mutate(management_SC_control =
           collapse_unique(management[which(crop_type == "SC" & density_factor == 1)]))%>% 
  ungroup %>% 
  # GET MANAGEMENT CONTROL IN  SC N0
  group_by(experiment_id,
           cultivar,#Take out N criteria an dinterrow criteria for corresponding N0
           interrow,
           P_amount) %>% 
  mutate(management_SC_N0_control =
           collapse_unique(management[which(crop_type == "SC" & density_factor == 1 &
                              N_factor == "N0")])) %>% 
  ungroup %>% 
  # Change "" in NA
  mutate(management_SC_control = 
           ifelse(management_SC_control == "", NA,
                  management_SC_control),
         management_SC_N0_control = 
           ifelse(management_SC_N0_control == "", NA,
                  management_SC_N0_control))

```

```{r set references SC crop, echo = FALSE}

data_work_control_crop <- data_work_yield_crop %>% 
  #GET MANAGEMENT CONTROL IN SC
  group_by(experiment_id,
           cultivar,
           N_factor,
           N_amount,
           interrow,
           P_amount) %>% 
  mutate(management_SC_control =
           collapse_unique(management[which(crop_type == "SC" & density_factor == 1)]))%>% 
  ungroup %>% 
  # GET MANAGEMENT CONTROL IN  SC N0
  group_by(experiment_id,
           cultivar,#Take out N criteria an dinterrow criteria for corresponding N0
           interrow,
           P_amount) %>% 
  mutate(management_SC_N0_control =
           collapse_unique(management[which(crop_type == "SC" & density_factor == 1 &
                              N_factor == "N0")]) ) %>% 
  ungroup %>% 
  # Change "" in NA
  mutate(management_SC_control = 
           ifelse(management_SC_control == "", NA,
                  management_SC_control),
         management_SC_N0_control = 
           ifelse(management_SC_N0_control == "", NA,
                  management_SC_N0_control))
```


For each IC management, we should have one corresponding management in SC. There may be some issues with corresponding SC (for ex: no corresponding SC found), so we investigate them.

## Look for IC with multiple corresponding managements in SC.

We should have one and only one corresponding management in SC for each IC. We look if there are issues.
```{r}


data_work_control %>%
   filter(stringr::str_detect(management_SC_control, "_")) %>%
  filter(crop_type == "IC") %>% 
  distinct(experiment_id, management) %>% 
  kable

```



No IC have multiple corresponding managements.

## Look for IC with multiple corresponding managements in SC N0.

We do the same thing for SC management in N0.
```{r}


data_work_control %>%
  filter(stringr::str_detect(management_SC_N0_control, "_")) %>%
  filter(crop_type == "IC") %>%
  distinct(experiment_id, management, management_SC_N0_control, interrow) %>%
  kable

```

Again, no IC have multiple corresponding N0 managements. 

## Look for IC for which there is no corresponding management in SC.

### N0

```{r IC no SC management}


data_work_control %>%
  filter(is.na(management_SC_control)) %>%
  filter(crop_type == "IC", N_factor == "N0") %>%
  distinct(experiment_id, management, species, cultivar, interrow) %>% 
  kable


```
These IC have no corresponding SC treatments because the corresponding SC cultivar have higher interrow distances (about 50cm):

```{r}

data_work_control %>% 
  filter(experiment_id %in% c("Auzeville_cochard_2010", "Auzeville_pk_2011"),
         cultivar %in% c("elmo", "castel", "irena"),
         crop_type == "SC") %>%
  distinct( experiment_id,species, crop_type, cultivar, interrow) %>% 
  kable

```

To go on, we do not take the criterion interrow into account to get SC control in these 2 experiments:

```{r}

management_SC_controls_special <- data_work_yield %>% 
  filter(experiment_id %in% c("Auzeville_cochard_2010", "Auzeville_pk_2011")) %>% 
  group_by(experiment_id,
           cultivar,
           N_factor,
           N_amount,
           P_amount) %>% 
  mutate(management_SC_control =
           collapse_unique(management[which(crop_type == "SC" & 
                                              density_factor == 1)])) %>% 
           ungroup %>%
  group_by(experiment_id,
           cultivar,
           P_amount) %>% 
    mutate(management_SC_N0_control =
           collapse_unique(management[which(crop_type == "SC" & 
                                              density_factor == 1 & N_factor == "N0")])) %>% 
  ungroup %>% 
  mutate(management_SC_control = 
           ifelse(management_SC_control == "", NA,
                                        management_SC_control),
         management_SC_N0_control = 
           ifelse(management_SC_N0_control == "", NA,
                                        management_SC_N0_control)) %>% 
           mutate(warning = "Different interrow")  #Add warning to warn about the difference.
         

data_work_control <- bind_rows(data_work_control %>% 
  filter(!((experiment_id %in% c("Auzeville_cochard_2010",
                                 "Auzeville_pk_2011")) )) %>%
    mutate(warning = NA), management_SC_controls_special) 
```


### Other N_factor

* Cereal

```{r}


data_work_control %>%
   filter(is.na(management_SC_control)) %>%
  filter(crop_type == "IC", N_factor != "N0", plant_family == "cereal") %>%
  distinct(experiment_id, management, N_amount, species) %>%
  kable(caption = "Cereals in IC that have no corresponding SC managements")

cereals_pb <- data_work_control %>%
   filter(is.na(management_SC_control)) %>%
  filter(crop_type == "IC", N_factor != "N0", plant_family == "cereal") %>%
  distinct(experiment_id, management,N_factor, N_amount, species) 

```

Some cereals in IC have no corresponding SC managements, in N fertilised management. 

```{r}



exp_ids_cereal_pb <- cereals_pb %>% 
  distinct(experiment_id) %>% pull

data_work_control %>% 
  filter(experiment_id %in% exp_ids_cereal_pb, crop_type == "SC", N_factor != "N0") %>% 
  distinct(experiment_id, management, density_level, density_factor,N_factor, N_amount) %>%
  kable(caption = "Different N amounts for SC managements.")

```

The managements in SC have different N amounts. We can not tackle this problem directly, so we cannot get the corresponding managements.


* Legumes

```{r}



data_work_control %>%
   filter(is.na(management_SC_control)) %>%
  filter(crop_type == "IC", N_factor != "N0", plant_family == "legume") %>% 
  select(experiment_id, management,N_factor, N_amount, species,management_SC_control) %>% 
  kable


legumes_pb <- data_work_control %>%
   filter(is.na(management_SC_control)) %>%
  filter(crop_type == "IC", N_factor != "N0", plant_family == "legume") %>%
  distinct(experiment_id, management,N_factor, N_amount, species) 




```

These legumes have no corresponding IC because many experiments have no legumes fertilized in SC.

```{r}



exp_ids_legumes_pb <- legumes_pb %>% 
  distinct(experiment_id) %>% pull

data_work_control %>%
  filter(experiment_id %in% exp_ids_legumes_pb,
         crop_type == "SC",
         N_factor != "N0", plant_family == "legume") %>%
  distinct(experiment_id, management, density_level,
           density_factor,N_factor, N_amount) %>%
  kable()

```


# Write the computed dataset



```{r, eval = FALSE}
management_control_IC_SC <- bind_rows(data_work_control, data_work_control_crop) %>% distinct(experiment_id, plant_family, species, management, management_SC_control, management_SC_N0_control)
```


```{r, echo=FALSE}
management_control_IC_SC%>% readr::write_rds('data/management_control_IC_SC.rds')
```


