---
title: "Ajustement non paramètrique des hauteurs"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r, include = FALSE, message=F}
library(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = F,
  warning = F,
  message = F
)

```

```{r}

# if(!"functions.helper"%in% installed.packages()){devtools::install_github("RemiMahmoud/functions.helper")}
library(functions.helper)
library(dplyr)
library(stringr)
library(tidyr)
library(purrr)
library(readr)
library(ggplot2)
theme_set(theme_bw())

# For missing data handling
library(naniar)
library(mice)
# library(sjmisc)
```



```{r set functions}

data_observations <- function(data_traits = data_traits_mean, trait ){
   data_traits %>%
  mutate(species = str_replace(species, "wheat_", "wheat ")) %>%
  filter(variable == trait) %>% 
  group_by(experiment_id, crop_id) %>% 
  mutate(n_measurements = n()) %>% 
  ungroup %>% 
  # filter(n_measurements >= 5) %>%
  filter(n_measurements >= 4) 
} 


which.customized <- function (x, arr.ind = FALSE, useNames = TRUE) 
{
    result = which(x, arr.ind = FALSE, useNames = TRUE)
    ifelse(identical(result, integer(0)), return(NA), return(result))
}



```



# Set data

```{r data_global}
# load trait database and index
data_traits_mean <- data.intercrop::traits_mean
index <- data.intercrop::index %>% mutate(crop_id = paste(management, year, plot_name, crop_type, species, cultivar, sep = "_")) 


data_asymp <- read_rds("data/data_asymp.rds")

data_asymp_wide <- data_asymp %>% 
  select(-time_thermal_asymp) %>% 
  pivot_wider(values_from = asymp, names_from = variable, names_prefix = "asymp_" )
```

```{r data biomass}
data_biomass_fits_raw <- read_rds("data/data_biomass_fit.rds") 
data_biomass_fits <-  data_biomass_fits_raw%>%
  rename_with(.fn = ~ paste0(.,"_biomass"), .cols = asymp:lambda) # Add biomass column suffix at columns


data_B_shoot <- data_observations(trait = "biomass_shoot")
data_B_shoot_asymp <- data_asymp %>% filter(variable == "biomass")

data_coordinates_slope_biomass <- data_biomass_fits_raw %>%
  distinct(experiment_id, crop_id, xslope, slope, y_at_slope, lambda)
```


```{r data height}

data_height_fits_raw <- read_rds("data/data_height_fit.rds")
data_height_fits <- data_height_fits_raw%>%
  rename_with(.fn = ~ paste0(.,"_height"), .cols = asymp:lambda) # Add height column suffix at columns

data_coordinates_slope_height <- data_height_fits_raw %>%
  distinct(experiment_id, crop_id, xslope, slope, y_at_slope, lambda)

data_height <-  data_observations(trait = "height")
data_height_asymp <- data_asymp %>% filter(variable == "height")

```


```{r data cover}


data_cover_fits_raw <- read_rds("data/data_cover_fit.rds")
data_cover_fits <- data_cover_fits_raw %>%
  rename_with(.fn = ~ paste0(.,"_cover"), .cols = asymp:lambda) # Add cover column suffix at columns

data_coordinates_slope_cover <- data_cover_fits_raw %>%
  distinct(experiment_id, crop_id, xslope, slope, y_at_slope, lambda)

data_cover <- data_observations(trait = "cover")
```

```{r data fits global}
data_fits <- full_join(data_height_fits, data_biomass_fits) %>% full_join(data_cover_fits)

data_fits_tidy <- data_fits %>% 
  pivot_longer(cols = matches("slope|lambda")) %>%
  separate(name, into = c("indicator", "trait"), sep = "_(?=biomass|height|cover)")

data_compute_indicators <- readr::read_rds("data/management_control_IC_SC.rds") %>% 
  left_join(index %>% select(experiment_id, management, contains("crop"), contains("species"), plant_family))



# data_fits_tidy %>% inner_join(index %>% distinct(crop_id, crop_type)) %>% filter(crop_type == "SC") %>% filter(!is.na(asymp_cover))
```

```{r}

data_yield_IC <- data_traits_mean %>% 
  filter(crop_type == "IC",variable == "biomass_seed") %>% 
  distinct(experiment_id, management, plant_family,  value, N_amount) %>% 
  rename(yield = value) %>% 
  group_by(experiment_id, management, plant_family, N_amount) %>% 
  summarise(yield = max(yield) ) %>% 
  ungroup %>% 
  pivot_wider(names_from = plant_family, values_from = yield, names_sep = "_") %>% 
  rename(yield_cereal = cereal, yield_legume = legume) %>% 
  mutate(yield_total = yield_cereal + yield_legume)


table_management_SC_control <- data_compute_indicators %>%
  distinct(experiment_id,crop_id, management, crop_type, plant_family, management_SC_control, management_SC_N0_control) %>% 
  mutate(management_control = ifelse(plant_family == "legume", management_SC_N0_control, management_SC_control)) %>% 
  distinct(experiment_id,crop_id, crop_type, plant_family, management, management_control) %>% 
  # pivot_wider(values_from = management_control, names_from = plant_family) %>% 
  group_by(experiment_id, management, crop_type) %>% 
  summarise(control_SC_cereal = management_control[which.customized(plant_family == "cereal")],
            control_SC_legume = management_control[which.customized(plant_family == "legume")]
            ) %>% 
  ungroup

```



# Fonctions imputation

```{r custom missing data function}

# Re-write functions of naniar to visualize NA according to factors

custom_coerce_fct_na_explicit <- function(x){
  if (is.factor(x) & anyNA(x)) {
    forcats::fct_explicit_na(x, na_level = "NA")
  } else {
    x
  }
}
custom_gg_miss_fct <- function(x, fct){
  
  fct <- rlang::enquo(fct)
  
  data <- x %>%
    # protect against error where grouping by missing value leads to
    # warning message from dplyr about explicit
    dplyr::mutate_at(vars(!!fct), .funs = custom_coerce_fct_na_explicit) %>%
    dplyr::group_by(!!fct) %>%
    miss_var_summary()
  
  ggobject <-
    ggplot(data,
           aes_string(x = quo_name(fct),
                      y = "variable",
                      fill = "pct_miss")) +
    geom_tile() +
    viridis::scale_fill_viridis(name = "% Miss") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45,
                                     hjust = 1))
  
  return(ggobject)
}


```


```{r function plot missing data factor}

# plot missing data according to a particular factor

plot_missing_data_factor <- function(data = data_to_impute, sp_mix = "wheat_turgidum_pea", fct = experiment_id){
  print(custom_gg_miss_fct(x = data %>% filter(species_mix == sp_mix) %>% select(-c(cultivar_mix, species_mix, N_fertilisation, management, crop_type)), fct = {{fct}}))
}


vis_miss_data <- function(data = data_to_impute, sp_mix = "wheat_turgidum_pea"){
  data %>% 
           filter(species_mix == sp_mix) %>%
           select(-c(experiment_id:crop_type, N_fertilisation)) %>% 
    vis_miss()
}

```


```{r function make predictor matrix}

# wrapper for predictor matrix in mice


make_custom_predictor_matrix <- function(data = data_to_impute, unused_columns = c("experiment_id", "management", "species_mix", "cultivar_mix", 
"crop_type")){
  
  # Do not use information as predictors in mice algorithm
  blocks <- make.blocks(colnames(data))
  pred_matrix <- make.predictorMatrix(data , blocks = blocks)
  
  index_unused_columns <- which(colnames(data) %in% unused_columns)
  
  pred_matrix[index_unused_columns,index_unused_columns] <- 0
  
  return(pred_matrix)
}


```


```{r}
compute_intra_IC_differences <- function(data){
  
  return(data%>%
           filter(crop_type == "IC") %>% 
           group_by(experiment_id, management, .imp) %>% 
           summarise(diff_slope_height = slope_height[which(plant_family == "cereal")] - slope_height[which(plant_family == "legume")],
                     diff_slope_biomass = slope_biomass[which(plant_family == "cereal")] - slope_biomass[which(plant_family == "legume")],
                     diff_lambda_height = lambda_height[which(plant_family == "cereal")] - lambda_height[which(plant_family == "legume")],
                     diff_lambda_biomass = lambda_biomass[which(plant_family == "cereal")] - lambda_biomass[which(plant_family == "legume")],
                     diff_asymp_height = asymp_height[which(plant_family == "cereal")] - asymp_height[which(plant_family == "legume")],
                     diff_asymp_biomass = asymp_biomass[which(plant_family == "cereal")] - asymp_biomass[which(plant_family == "legume")],
                     slope_biomass_cereal  = slope_biomass[which(plant_family == "cereal")],
                     slope_biomass_legume  = slope_biomass[which(plant_family == "legume")],
                     lambda_biomass_cereal  = lambda_biomass[which(plant_family == "cereal")],
                     lambda_biomass_legume  = lambda_biomass[which(plant_family == "legume")],
                     asymp_biomass_cereal  = asymp_biomass[which(plant_family == "cereal")],
                     asymp_biomass_legume  = asymp_biomass[which(plant_family == "legume")],
                     slope_height_cereal  = slope_height[which(plant_family == "cereal")],
                     slope_height_legume  = slope_height[which(plant_family == "legume")],
                     lambda_height_cereal  = lambda_height[which(plant_family == "cereal")],
                     lambda_height_legume  = lambda_height[which(plant_family == "legume")],
                     asymp_height_cereal  = asymp_height[which(plant_family == "cereal")],
                     asymp_height_legume  = asymp_height[which(plant_family == "legume")],
                     .groups = "drop"))
  
}
compute_IC_SC_differences <- function(data_compute_indicators, data_imputed, data_yield_IC){
  
  data_output <- data_compute_indicators %>%
    distinct(experiment_id, crop_id, crop_type, density_relative,
             plant_family, species, species_mix,
             cultivar, cultivar_mix,N_factor, management,
             management_SC_control, management_SC_N0_control, 
             value_SC_N0_control, value_SC_control) %>% 
    # inner_join(data_fits %>% select(experiment_id, crop_id, matches("slope|lambda"))) %>% 
    inner_join(data_imputed %>%
                 select(experiment_id, crop_id, .imp, matches("slope|lambda|asymp"))) %>% 
    mutate(management_control = ifelse(plant_family == "legume",
                                       management_SC_N0_control,
                                       management_SC_control)) %>%  # SC control is N0 for legume
    # group_by(experiment_id, management_SC_N0_control) %>% 
    group_by(experiment_id, management_control, .imp) %>% 
    mutate(
      slope_height_SC_control = unique(slope_height[which.customized(management == management_control &
                                                                       cultivar == cultivar)]),
      lambda_height_SC_control = unique(lambda_height[which.customized(management == management_control &
                                                                         cultivar == cultivar)]),
      asymp_height_SC_control = unique(asymp_height[which.customized(management == management_control &
                                                                       cultivar == cultivar)]),
      slope_biomass_SC_control = unique(slope_biomass[which.customized(management == management_control &
                                                                         cultivar == cultivar)]),
      lambda_biomass_SC_control = unique(lambda_biomass[which.customized(management == management_control &
                                                                           cultivar == cultivar)]),
      asymp_biomass_SC_control = unique(asymp_biomass[which.customized(management == management_control &
                                                                         cultivar == cultivar)])
      # ,
      # yield_SC_control = ifelse(plant_family == "legume",
      #                           mean(value_SC_N0_control, na.rm=TRUE),
      #                           mean(value_SC_control, na.rm=TRUE))
       ) %>% 
    ungroup  %>% 
    mutate(
      diff_slope_height = slope_height - slope_height_SC_control,
      diff_lambda_height = lambda_height - lambda_height_SC_control,
      diff_asymp_height = asymp_height - asymp_height_SC_control,
      diff_slope_biomass_n = (slope_biomass/as.numeric(density_relative)) - slope_biomass_SC_control,
      diff_slope_biomass = slope_biomass - slope_biomass_SC_control,
      diff_lambda_biomass = lambda_biomass - lambda_biomass_SC_control,
      diff_asymp_biomass_n = (asymp_biomass/as.numeric(density_relative)) - asymp_biomass_SC_control,
      diff_asymp_biomass = asymp_biomass - asymp_biomass_SC_control,
      # diff_normalized_slope_height =
      #   (slope_height - slope_height_SC_control)/pmax(slope_height,slope_height_SC_control ),
      # diff_normalized_lambda_height =
      #   (lambda_height - lambda_height_SC_control)/pmax(lambda_height, lambda_height_SC_control),
      # diff_normalized_asymp_height =
      #   (asymp_height - asymp_height_SC_control)/pmax(asymp_height, asymp_height_SC_control),
      # diff_normalized_slope_biomass = 
      #   (slope_biomass - slope_biomass_SC_control)/pmax(slope_biomass, slope_biomass_SC_control),
      # diff_normalized_lambda_biomass = 
      #   (lambda_biomass - lambda_biomass_SC_control)/pmax(lambda_biomass, lambda_biomass_SC_control),
      # diff_normalized_asymp_biomass = 
      #   (asymp_biomass - asymp_biomass_SC_control)/pmax(asymp_biomass, asymp_biomass_SC_control)
    ) %>%
    filter(crop_type == "IC") %>% 
    inner_join(data_yield_IC) %>%
  select(experiment_id, management,.imp,  cultivar_mix, species_mix, plant_family,contains("diff")) %>%
  pivot_wider(names_from = plant_family, values_from = contains("diff")) %>%
  rename_with(.fn =  ~stringr::str_replace(., "diff", "diff_IC_SC"),
              .cols =contains('diff'))
  
  return(data_output)
}


make_data_predictors <- function(data_intra_IC, data_IC_SC, data_yield_IC){
  data_output <- data_intra_IC %>%
  select(-contains("y_at_slope"),
         -contains("xslope"),
         -contains("lambda_cereal_cover"),
         -contains("lambda_legume_cover"),
         -contains("slope_cereal_cover"),
         -contains("slope_legume_cover"),
         -contains("diff_lambda_cover"),
         -contains("diff_asymp_cover"),
         -matches("diff_weighted_slope_biomass|diff_weighted_slope_height"),
         -contains("index_slope"))%>% 
    left_join(data_IC_SC) %>% 
    left_join(data_yield_IC)
  
  return(data_output)
}

```



# Impute parameters

```{r}


data_impute <- data_fits %>%
  left_join(index %>% 
              distinct(crop_id,crop_type, management, experiment_id, plant_family, species_mix, species)) %>% 
  select(experiment_id, crop_id, crop_type, management,plant_family, species_mix, species, matches("^slope"),
         matches("lambda")) %>% 
  left_join(data_asymp_wide)

vis_miss(data_impute %>% select(-c(experiment_id:species)))
custom_gg_miss_fct(data_impute, experiment_id)
custom_gg_miss_fct(data_impute, species_mix)
gg_miss_upset(data_impute, nintersects = NA , nsets= 1000)

```


## Wheat turgidum / pea


### Inspect missing values

```{r}

# pattern wt pea
data_wt_pea <- data_impute %>% 
  filter(species_mix %in% c("wheat_turgidum", "pea", "wheat_turgidum_pea") & experiment_id %in%c("Auzeville_marinette_1_2015", "Auzeville_SGs_2007", "Auzeville_TE_2006", 
"Auzeville_TO_2013", "Auzeville_ZN_2012")) %>% 
  select(-c(species_mix, contains("cover")))

custom_gg_miss_fct(data_wt_pea, fct = experiment_id)
custom_gg_miss_fct(data_wt_pea, fct = species)


vis_miss(data_wt_pea)



data_wt_pea %>%
  gg_miss_upset(nsets = 20)

```

Experimental units from Auzeville marinette 2015 have missing values for biomass, and so for Auzeville 2013 as they do not have dynamic measurements. This represents 20% missing values. However, slopes are correlated to maximal values so that we can impute missing data.

### Perform imputation

```{r}

mids_wt_pea <- mice::mice(data_wt_pea%>% select(-c(crop_id, experiment_id, management)) %>% mutate(crop_type = as.factor(crop_type), plant_family = as.factor(plant_family)), m = 10, method = "norm.nob")

mids_wt_pea$predictorMatrix
# mids_wt_pea$where


densityplot(mids_wt_pea)
densityplot(mids_wt_pea, ~slope_biomass|plant_family)
densityplot(mids_wt_pea, ~lambda_biomass|plant_family)

data_wt_pea_imputed <- data_wt_pea %>% 
  select(c(crop_id, experiment_id, management, plant_family) ) %>%
  mutate(.id = 1:n()) %>% 
  right_join(as_tibble(complete(mids_wt_pea, action = "long")))

# data_wt_pea_imputed


```

### Visualize imputation

```{r}
data_wt_pea_imputed %>%
  group_by(crop_id) %>% 
  mutate(imputed = ifelse(slope_biomass[1] != slope_biomass[2], "Imputed", "Raw")) %>% # Make a bool to know if data was imputed or not
  ungroup %>% 
  pivot_longer(contains("biomass")) %>% 
  filter(name == "slope_biomass") %>% 
  ggplot(aes(x = value)) + 
  geom_density(aes(group = .imp)) +
  # facet_grid(name~species, scales= "free" ) + 
  facet_wrap(species~imputed, ncol = 2)
```


### Compute differences

```{r}
### Intra-IC
data_wt_pea_intra_IC <- data_wt_pea_imputed %>% compute_intra_IC_differences()
# data_wt_pea_intra_IC %>%
#   group_by(experiment_id, management) %>% 
#   mutate(imputed = diff_slope_biomass[1] != diff_slope_biomass[2]) %>% 
#   ungroup %>% 
#   pivot_longer(contains("biomass")) %>% 
#   filter(name == "diff_slope_biomass") %>% 
#   ggplot(aes(x = value)) + 
#   geom_density(aes(group = .imp)) +
#   # facet_grid(name~species, scales= "free" ) + 
#   facet_wrap(.~imputed, ncol = 1)
## Inter-IC-SC

data_wt_pea_inter_IC_SC_wt_pea <-  compute_IC_SC_differences(data_compute_indicators, data_wt_pea_imputed, data_yield_IC)

data_predictors_wt_pea <- make_data_predictors(data_wt_pea_intra_IC, data_wt_pea_inter_IC_SC_wt_pea, data_yield_IC )

```




## Wheat turgidum / fababean


### Inspect missing values

```{r}

# pattern wt fababean
data_wt_fababean <- data_impute %>% 
  filter(species_mix %in% c("wheat_turgidum", "fababean", "wheat_turgidum_fababean") & experiment_id %in%c("Auzeville_cochard_2010", "Auzeville_pk_2011", "Auzeville_PP_2011", 
"Auzeville_TO_2013", "Auzeville_ZN_2012")) %>% 
  select(-c(species_mix, contains("cover")))

custom_gg_miss_fct(data_wt_fababean, fct = experiment_id)
custom_gg_miss_fct(data_wt_fababean, fct = species)

vis_miss(data_wt_fababean)

```
Few missing values. They come from Auzeville 2013, in 20% of the experimental units

### Perform imputation

```{r}

mids_wt_fababean <- mice::mice(data_wt_fababean%>% select(-c(crop_id, experiment_id, management)) %>% mutate(crop_type = as.factor(crop_type), plant_family = as.factor(plant_family)), m = 10, method = "norm")

# mids_wt_fababean$predictorMatrix
# mids_wt_fababean$where


densityplot(mids_wt_fababean)
densityplot(mids_wt_fababean, ~slope_biomass|plant_family)
densityplot(mids_wt_fababean, ~lambda_biomass|plant_family, scales=  list(x = "free", y= "free"))


data_wt_fababean_imputed <- data_wt_fababean %>% select(c(crop_id, experiment_id, management, plant_family) ) %>% mutate(.id = 1:n()) %>% right_join(as_tibble(complete(mids_wt_fababean, action = "long")))

# data_wt_fababean_imputed


```

### Visualize imputation

```{r}
data_wt_fababean_imputed %>%
  group_by(crop_id) %>% 
  mutate(imputed = slope_biomass[1] != slope_biomass[2]) %>% 
  ungroup %>% 
  pivot_longer(contains("biomass")) %>% 
  filter(name == "slope_biomass") %>% 
  ggplot(aes(x = value)) + 
  geom_density(aes(group = .imp)) +
  # facet_grid(name~species, scales= "free" ) + 
  facet_wrap(species~imputed, ncol = 2)
```


### Compute differences

```{r}
### Intra-IC
data_wt_fababean_intra_IC <- data_wt_fababean_imputed %>% compute_intra_IC_differences()

data_wt_fababean_inter_IC_SC_wt_fababean <-  compute_IC_SC_differences(data_compute_indicators, data_wt_fababean_imputed, data_yield_IC)

data_predictors_wt_fababean <- make_data_predictors(data_wt_fababean_intra_IC, data_wt_fababean_inter_IC_SC_wt_fababean, data_yield_IC )

```





# Write data





```{r}

data_all_predictors <- bind_rows(data_predictors_wt_fababean, data_predictors_wt_pea)

write_rds(x = data_all_predictors, "data/data_all_diff_with_imputations.rds")

```




